\documentclass{article}

\usepackage[a4paper,margin=2.5cm]{geometry}
\usepackage[
  theorems=true,
  plots=true,
  minted=true,
  glossaries=true,
  fontset=lmodern
]{trymtex}

\title{\texttt{trymtex} Package Manual}
\author{Trym S\ae ther}
\date{\today}

\begin{document}
\maketitle
\tableofcontents
\vspace{1cm}

\section{Introduction}
The \texttt{trymtex} package is a collection of modular settings, helpers, and default styles tailored for general-purpose \LaTeX{} document authoring. It simplifies the preamble by loading often-used packages and standardizing document layouts, theorem environments, and math macros.

\section{Usage and Options}
To use the package, simply include it in your preamble:
\begin{verbatim}
\usepackage[<options>]{trymtex}
\end{verbatim}

\subsection{Package Options}
You can customize the package layout and loaded modules by passing key-value options:
\begin{itemize}
  \item \texttt{fontset}: Selects the document font. Options include \texttt{lmodern} (default), \texttt{pagella}, \texttt{ibmplex}, \texttt{fira}, or \texttt{none}.
  \item \texttt{theorems}: (boolean) Loads and styles customized theorem environments.
  \item \texttt{plots}: (boolean) Loads pgfplots and tikz setups.
  \item \texttt{minted}: (boolean) Loads code-listing capabilities (requires \texttt{--shell-escape}).
  \item \texttt{biblatex}: (boolean) Loads bibliography management tools (defaults to false).
\end{itemize}

\section{Math Enhancements}
The math module provides numerous semantic macros, ensuring standard presentation of mathematical notation.

For instance, norms and absolute values are simplified: Let \( x \in \RR^n \), then its norm and absolute components can be denoted as
\[
  \norm{x} \quad \text{and} \quad \abs{x_i}.
\]

\section{Theorem Environments}
When the \texttt{theorems} option is \texttt{true}, \texttt{trymtex} introduces elegant layouts for definitions, theorems, lemmas, etc., handled via \texttt{tcolorbox}.

\begin{definition}{Metric Space}{metric-space}
  A metric space is a pair \( (X,d) \) where \( X \) is a set and \( d \) is a metric satisfying the conditions of non-negativity, identity of indiscernibles, symmetry, and the triangle inequality.
\end{definition}

\begin{theorem}{Positive Squares}{tiny-thm}
  For all \( x \in \RR \), one has \( x^2 \ge 0 \).
\end{theorem}

\begin{proof}
  This follows directly from the axioms of ordered fields.
\end{proof}

\section{Custom Boxes}
The \texttt{boxes} module defines visually distinct semantic boxes for asides and warnings using customized \texttt{tcolorbox} environments.

\begin{filingbox}{Note on Files}
  This is a standard informational filing box. Use it to provide context or metadata.
\end{filingbox}

\begin{railingbox}{Warning/Caution}
  The railing box draws attention to critical issues or warnings in the text.
\end{railingbox}

\begin{flagbox}{Checkpoint}
  Use the flag box to mark milestones, tips, or goals within your text.
\end{flagbox}

\end{document}
